Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-15 ms/manuscript.Rmd
Continue using image folder for now

```{r traits-used-image, fig.height = 9, fig.width = 6, fig.cap = "Examples of traits used in this study."}
knitr::include_graphics(here::here("ms/Fig_1.pdf"))
```

>>>>

```{r traits-used-image, fig.height = 9, fig.width = 6, fig.cap = "Examples of traits used in this study."}
knitr::include_graphics(here::here("images/Figure_3_1_traits_lowres.pdf"))
```
